\documentclass[a5paper,10pt]{memoir}
% Packages
\usepackage[nobottomtitles]{titlesec}
\usepackage{fontspec}
\setmainfont{TeX Gyre Pagella} %palatino clone
\usepackage[yyyymmdd,hhmmss]{datetime}
\usepackage{microtype}
\usepackage[british, latin]{babel}
\usepackage[]{gitinfo2}
% local
\usepackage{rubrics}
\usepackage{styling}
% Config
\copypagestyle{versionplain}{plain}
\newcommand{\version}{\tiny Release: v1.0.0 (template v2.1.1)}
\makeevenfoot{versionplain}{\thepage}{}{\version}
\makeoddfoot{versionplain}{\version}{}{\thepage}
\pagestyle{versionplain}
\thispagestyle{empty}
% layout
\setulmarginsandblock{0.5in}{0.7in}{*}
\setlrmarginsandblock{0.5in}{0.5in}{*}
\checkandfixthelayout
% headers
\setsecnumdepth{chapter}
\setsecheadstyle{\Large\scshape\raggedright\centering}
\setafterparaskip{1.5ex plus .2ex}

\begin{document}
\let\per\relax

\input{propers}

\begin{center}
  {\LARGE \masstype}

  ~

  {\Large\scshape \feast}

  \greseparator{2}{10}
\end{center}

% 
\section{Office}
\black{
  \l{\office}
  \e{\officeTranslation}
}
% 

\section{Collect}
\black{\collect}

\section{Lesson}
In those days, the wicked Jews said one to another, "Come, and let us invent
devices against the just; for the law shall not perish from the priest, nor
counsel from the wise, nor the word from the prophet; come, and let us
strike him with the tongue and let us give no heed to all his words." Give
heed to me, O Lord, and hear the voice of my adversaries. Shall evil be
rendered for good, because they have digged a pit for my soul? Remember that
I have stood in Your sight, to speak good for them; and to turn away Your
indignation from them. Therefore deliver up their children to famine, and
bring them into the hands of the sword: let their wives be bereaved of
children, and widows, and let their husbands be slain by death; let their
young men be stabbed with the sword  in battle. Let a cry be heard out of
their houses, for You shall bring the robber upon them suddenly, because
they have digged a pit to take me, and have hid snares for my feet. But You,
O Lord, know all their counsel against me unto death; forgive not their
iniquity, and let not their sin be blotted out from Your sight.  Let them be
overthrown before Your eyes; in the time of Your wrath destroy them, O Lord
our God.

% 
\section{Responsory}
\black{
  \l{\responsory}
  \e{\responsoryTranslation}
}
% 

\section{Gospel}
    At that time, the chief priests planned to put Lazarus to death also. For on
    his  account many of the Jews began to leave them and to believe in
    Jesus. Now the next day, the great crowd which had come to the feast, when
    they heard that Jesus was coming to Jerusalem, took the branches of palms
    and went forth to meet Him. And they cried out, ``Hosanna! Blessed is He
    who comes in the name of the Lord, the King of Israel!'' And Jesus found a
    young ass, and sat upon it, as it is written, ``Fear not, daughter of Sion;
    behold, your King comes, sitting upon the colt of an ass.'' These things His
    disciples did not at first understand. But when Jesus was glorified, then
    they remembered that these things were written about Him, and that they had
    done these things to Him.  The crowd therefore, which was with Him when He
    called Lazarus from the tomb and raised him from the dead, bore witness to
    Him. And the reason why the crowd also went to meet Him was that they
    heard that He had worked this sign. The Pharisees therefore said among
    themselves, ``Do you see that we avail nothing?  Behold, the entire world has
    gone after Him!'' Now there were certain Gentiles among those who had gone
    up to worship on the feast. These therefore approached Philip, who was from
    Bethsaida of Galilee, and asked him, saying, ``Sir, we wish to see Jesus.''
    Philip came and told Andrew; again, Andrew and Philip spoke to Jesus. But
    Jesus answered them, ``The hour has come for the Son of Man to be
    glorified. Amen, amen, I say to you, unless the grain of wheat falls into
    the ground and dies, it remains alone. But if it dies, it brings forth much
    fruit. He who loves his life, loses it; and he who hates his life in this
    world keeps it unto life everlasting.  If anyone serves Me, let him follow
    Me; and where I am there also shall My servant be. If anyone serves Me, My
    Father will honor him. Now my soul is troubled.  And what shall I say?
    Father, save Me from this hour! No, this is why I came to this
    hour. Father, glorify Your name!'' There came therefore a voice from heaven,
    ``I have both glorified it, and I will glorify it again.''  Then the crowd
    which was standing round and had heard, said that it had thundered. Others
    said, ``An angel has spoken to Him.'' Jesus answered and said, ``Not for Me
    did this voice come, but for you. Now is the judgment of the world; now
    will the prince of the world be cast out. And I, if I be lifted up from the
    earth, will draw all things to Myself.'' Now He said this signifying by what
    death He was to die. The crowd answered Him, ``We have heard from the Law
    that the Christ abides forever. And how can You say, `The Son of Man must be
    lifted up'? Who is this Son of Man?''  Jesus therefore said to them, ``Yet a
    little while the light is among you. Walk while you have the light, that
    darkness may not overtake you. He who walks in the darkness does not know
    where he goes. While you have the light, believe in the light, that you may
    become sons of light.'' These things Jesus spoke, and He went away and hid
    Himself from them.

\section{Offertory}
\black{
  \l{\offertory}
  \e{\offertoryTranslation}
}

\section{Communion}
\black{
  \l{\communion}
  \e{\communionTranslation}
}

\section{Post Communion}
\black{\postcommunion}

\vfill
{
\tiny
Typeset by John Morris in ten-point Palatino.  Translations from the
Knox Bible, divinumofficium.com, the St. Dominic Missal, and my own.

% 
The latest version of this booklet can always be found at
\url{ https://github.com/2e0byo/StCuthbertsMasses }. Comments?
Suggestion? Found a mistake? Open an issue in the repository.
% 
}
\section{Marian Antiphon}
\red{At the conclusion of Mass the Marian antiphon proper to the season is sung:}
% \grechangestaffsize{15}
\gregorioscore{marian}
% 
% \vfill

% \red{A motet or hymn may follow.}
% \begin{center}
%   \+
% \end{center}


% 

% {\centering\footnotesize\texttt{Compositum \today\ hora \currenttime}\par}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-engine: luatex
%%% End:
