% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{Sabbato post Dominicam Passionis}
\newcommand{\masstype}{ Missa Cantata%
  % 
  Iuxta Ritum Dominicanum%
  % %
}
% 
\newcommand{\office}{%
  Miserere mihi, Domine, quoniam tribulor: libera me, et eripe me de manibus
  inimicorum meorum, et a persequentibus. me: Domine non confundar, quoniam
  invocavi te. \v\ In te Domine speravi, non confundar in aetemum: in justitia
  tua libera me.
}

\newcommand{\officeTranslation}{%
  Have mercy on me, O Lord, for I am afflicted; deliver me out of the hands of
  my enemies, and from them who persecute me; let me not be confounded, O Lord,
  for I have called upon You. \v\ In You, O Lord, I have hoped, let me never be
  confounded; deliver me in Your justice.
}

% 
\newcommand{\collect}{%
  \l{%
    Proficiat, quaesumus Domine, plebs tibi dicata piae devotionis affectu, ut
    sacris actionibus erudita, quanto majestati tuae fit gratior, tanto donis
    potioribus augeatur.
  }
  \e{%

    May the people, dedicated to You, grow in the desire of holy love, O Lord,
    we pray; so that schooled in these sacred mysteries, they may, as they are
    endowed with greater gifts, become more acceptable to Your majesty
    }
    \per
}

\newcommand{\lesson}{%

  \l{%

    In diebus illis: Dixerunt impii Judaei ad invicem: Venite, et cogitemus
    contra justum cogitationes: non enim peribit lex a sacerdote, neque
    consilium a sapiente, nec sermo a propheta. Venite, et percutiamus eum
    lingua, et non attendamus ad universos sermones ejus.  Attende, Domine, ad
    me, et audi vocem adversariorum meorum. Numquid redditur pro bono
    malum, quia foderunt foveam animae meae? Recordare quod steterim in
    conspectu tuo, ut loquerer pro eis: bonum, et averterem indignationem
    tuam ab eis. Propterea da filios eorum in famem, et deduc eos in manus
    gladii; fiant uxores eorum absque liberis, et viduae; et viri earum
    interficiantur morte; juvenes eorum confodiantur gladio in proelio. Audiatur
    clamor de domibus eorum; adduces enim super eos Iatronem repente, quia
    foderunt foveam ut caperent me, et laqueos absconderunt pedibus meis. Tu
    autem, Domine, scis omne consilium eorum adversum me in mortem: ne
    propitieris iniquitati eorum, et peccatum eorum a facie tua non deleatur:
    fiant corruentes in conspectu tuo in tempore furoris tui abutere eis,
    Domine Deus noster.
  }
  \e{%
    In those days, the wicked Jews said one to another, "Come, and let us invent
    devices against the just; for the law shall not perish from the priest, nor
    counsel from the wise, nor the word from the prophet; come, and let us
    strike him with the tongue and let us give no heed to all his words." Give
    heed to me, O Lord, and hear the voice of my adversaries. Shall evil be
    rendered for good, because they have digged a pit for my soul? Remember that
    I have stood in Your sight, to speak good for them; and to turn away Your
    indignation from them. Therefore deliver up their children to famine, and
    bring them into the hands of the sword: let their wives be bereaved of
    children, and widows, and let their husbands be slain by death; let their
    young men be stabbed with the sword  in battle. Let a cry be heard out of
    their houses, for You shall bring the robber upon them suddenly, because
    they have digged a pit to take me, and have hid snares for my feet. But You,
    O Lord, know all their counsel against me unto death; forgive not their
    iniquity, and let not their sin be blotted out from Your sight.  Let them be
    overthrown before Your eyes; in the time of Your wrath destroy them, O Lord
    our God.
  }

}

% 
\newcommand{\responsory}{%
  Pacifice loquebantur mihi inimici mei: et in ira molesti erant mihi. \v\ Vidisti Domine Deus meus,
  ne sileas: ne discedas a me. 
}
\newcommand{\responsoryTranslation}{%
 My enemies spoke peaceably to me, and in anger they were troublesome to me. \v\
 You have seen, O Lord, my God, be not silent; depart not from me.
}
% 
\newcommand{\gospel}{%
  \l{%
    In illo tempore: Cogitaverunt principes sacerdotum ut et Lazarum
    interficerent, quia multi propter ilium abibant ex Judaeis et credebant in
    Jesum. In crastinum autem turba multa, quae venerat ad diem festum, cum
    audissent quia venit Jesus Jerosolymam, acceperunt ramos pahnarum, et
    processerunt obviam ei, et clamabant: Hosanna, benedictus qui venit in
    nomine Domini, rex Israel!  Et invenit Jesus asellum, et sedit super eum,
    sicut scriptum est: Noli timere, filia Sion: ecce rex tuus venit sedens
    super pullum asinae. Haec non cognoverunt discipuli ejus primum: sed quando
    glorificatus est Jesus, tune recordati sunt quia haec erant scripta de eo,
    et haec fecerunt ei. Testimonium ergo perhibebat turba quae erat cum eo
    quando Lazarum vocavit de monumento, et suscitavit eum a mortuis. Propterea
    et obviam venit ei turba, quia audierunt eum fecisse hoc signum. Pharisaei
    ergo dixerunt ad semetipsos: Videtis quia nihil proficimus? ecce mundus
    totus post eum abiit. Erant autem quidam Gentiles ex his, qui ascenderant ut
    adorarent in die festo. Hi ergo accesserunt ad Philippum, qui erat a
    Bethsaida Galilaeae, et rogabant eum, dicentes: Domine, volumus Jesum
    videre. Venit Philippus, et dicit Andreae. Andreas rursum et Philippus
    dixerunt Jesu. Jesus autem respondit eis, dicens: Venit hora, ut
    clari:ficetur Filius hominis. Amen, amen, dico vobis, nisi granum frumenti
    cadens in terram, mortuum fuerit, ipsum solum manet. Si aritem mortuum
    fuerit, multum fructum affert. Qui amat animam suam, perdet eam; et qui odit
    animam suam in hoc mundo, in vitam aeternam custodit eam. Si quis mihi
    ministrat, me sequatur; et ubi sum ego, illic et minister meus erit. Si quis
    mihi ministraverit, honorificabit eum Pater mens. Nunc anima mea turbata
    est. Et quid dicam? Pater, salvifica me ex hac hora.  Sed propterea veni in
    horam hanc. Pater, clarifica nomen tuum. Venit ergo vox de caelo: Et
    clarificavi, et iterum clarificabo. Turba ergo, quae stabat et audierat,
    dicebat tonitruum esse factum. Alli dicebant: Angelus ei locutus
    est. Respondit Jesus, et dixit: Non propter me haec vox venit, sed propter
    vos. Nunc judicium est mundi: nunc princeps hujus mundi ejicietur foras. Et
    ego, si exaltatus fuero a terra, omnia traham ad meipsum. (Hoc autem dice
    bat, significans qua morte esset moriturus.) Respondit ei turba: Nos
    audivimus ex lege, quia Christus manet in aetemum; et quomodo tu dicis:
    Oportet exaltari Filium hominis? Quis est iste filius hominis? Dixit ergo
    eis Jesus: Adhuc modicum lumen in vobis est. Ambulate dum lucem habetis, ut
    non vos tenebrae comprehendant; et qui ambulat in tenebris, nescit quo
    vadat. Dum lucem habetis, credite in lucem, ut :filii lucis sitis. Haec
    locutus est Jesus: et abiit, et abscondit se ab eis.
  }
  \e{%

    At that time, the chief priests planned to put Lazarus to death also. For on
    his  account many of the Jews began to leave them and to believe in
    Jesus. Now the next day, the great crowd which had come to the feast, when
    they heard that Jesus was coming to Jerusalem, took the branches of palms
    and went forth to meet Him. And they cried out, ``Hosanna! Blessed is He
    who comes in the name of the Lord, the King of Israel!'' And Jesus found a
    young ass, and sat upon it, as it is written, ``Fear not, daughter of Sion;
    behold, your King comes, sitting upon the colt of an ass.'' These things His
    disciples did not at first understand. But when Jesus was glorified, then
    they remembered that these things were written about Him, and that they had
    done these things to Him.  The crowd therefore, which was with Him when He
    called Lazarus from the tomb and raised him from the dead, bore witness to
    Him. And the reason why the crowd also went to meet Him was that they
    heard that He had worked this sign. The Pharisees therefore said among
    themselves, ``Do you see that we avail nothing?  Behold, the entire world has
    gone after Him!'' Now there were certain Gentiles among those who had gone
    up to worship on the feast. These therefore approached Philip, who was from
    Bethsaida of Galilee, and asked him, saying, ``Sir, we wish to see Jesus.''
    Philip came and told Andrew; again, Andrew and Philip spoke to Jesus. But
    Jesus answered them, ``The hour has come for the Son of Man to be
    glorified. Amen, amen, I say to you, unless the grain of wheat falls into
    the ground and dies, it remains alone. But if it dies, it brings forth much
    fruit. He who loves his life, loses it; and he who hates his life in this
    world keeps it unto life everlasting.  If anyone serves Me, let him follow
    Me; and where I am there also shall My servant be. If anyone serves Me, My
    Father will honor him. Now my soul is troubled.  And what shall I say?
    Father, save Me from this hour! No, this is why I came to this
    hour. Father, glorify Your name!'' There came therefore a voice from heaven,
    ``I have both glorified it, and I will glorify it again.''  Then the crowd
    which was standing round and had heard, said that it had thundered. Others
    said, ``An angel has spoken to Him.'' Jesus answered and said, ``Not for Me
    did this voice come, but for you. Now is the judgment of the world; now
    will the prince of the world be cast out. And I, if I be lifted up from the
    earth, will draw all things to Myself.'' Now He said this signifying by what
    death He was to die. The crowd answered Him, ``We have heard from the Law
    that the Christ abides forever. And how can You say, `The Son of Man must be
    lifted up'? Who is this Son of Man?''  Jesus therefore said to them, ``Yet a
    little while the light is among you. Walk while you have the light, that
    darkness may not overtake you. He who walks in the darkness does not know
    where he goes. While you have the light, believe in the light, that you may
    become sons of light.'' These things Jesus spoke, and He went away and hid
    Himself from them.

  }
}
\newcommand{\offertory}{%
  Benedictus es Domine, doce me justificationes tuas, et non tradas
  calumniantibus me superbis: et respondebo exprobrantibus mihi verbum.
}
\newcommand{\offertoryTranslation}{%
  Blessed are You, O Lord, teach me Your justifications, and deliver me not up
  to the proud who calumniate me; and I will answer a word to those who upbraid
  me.
}
\newcommand{\secret}{%
  \l{%
    A cunctis nos, quaesumus Domine; reatibus et periculis propitiatus absolve,
    quos tanti mysterii tribuis esse consortes.
  }
  \e{%
    We beseech You, O Lord, in Your mercy, set free from all sins and dangers
    those whom You make partakers of so great a mystery:
  }
  \per
}
\newcommand{\communion}{%
  Ne tradideris me, Domine, in animas persequentium me: quoniam insurrexerunt in
  me testes iniqui et mentita est iniquitas sibi.
}
\newcommand{\communionTranslation}{%
  O Lord, deliver me not over to the souls of those who persecute me; for unjust
  witnesses have risen up against me, and iniquity has lied to itself.
}
\newcommand{\postcommunion}{%
  \l{%
    Divini muneris largitate satiati, quaesumus Domine Deus noster, ut hujus
    semper participatione vivamus.
  }
  \e{%
    Filled with the bounty of Your divine gift, we beseech You, 0 Lord our God,
    that we may ever live by sharing in the same
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../DominicanOrdinaries/masses/5/kyrie}
\newcommand{\gloriaPath}{../DominicanOrdinaries/masses/5/gloria}
\newcommand{\sanctusPath}{../DominicanOrdinaries/masses/5/sanctus}
\newcommand{\agnusPath}{../DominicanOrdinaries/masses/5/agnus}
\newcommand{\itePath}{../DominicanOrdinaries/masses/5/ite}
% 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
