% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{S. Scholasticae}
\newcommand{\masstype}{ Missa Cantata%
  % 
  Iuxta Ritum Dominicanum%
  % %
}
% 
\newcommand{\office}{%
  Gaudeamus omnes in Domino, diem festum
  celebrantes sub honore beatae Scholasticæ, virginis de cujus solemnitate gaudent angeli, et collaudant Filium Dei. 
  Eructavit cor meum verbum bonum: dico ego
  opera mea regi. 
}
\newcommand{\officeTranslation}{%
  Let us all rejoice in the Lord, celebrating a
  festival day in honor of the blessed virgin Scholastica,
  on whose
  solemnity the angels rejoice, and give praise to the
  Son of God.  My
  heart has uttered a good word; I speak my works to the
  king.
}
% 
\newcommand{\collect}{%
  \l{%
    Deus, qui animam beatae virginis tuae Scholasticae, ad ostendendam innocentiae viam, in columbae
    specie caelum penetrare fecisti; da nobis ejus meritis et
    precibus, ita innocenter vivere, ut ad aetema mereamur
    gaudia pervenire.
  }
  \e{%
    O God, who to show the way of the innocent
    made the soul of Your virgin, blessed Scholastica, enter heaven in the likeness of a dove; grant to us,
    through her merits and prayers, to live in such innocence as to be worthy to attain everlasting joys:
  }
  \per
}
\newcommand{\lesson}{%
  \l{%
    Brethren: "He
    who boasts, let him boast in the Lord." For he is not
    approved who commends himself, but he whom the
    Lord commends. Would to God that you could bear
    with a little of my foolishness! Nay, do bear with me!
    For I am jealous for you with a divine jealousy. For I
    betrothed you to one spouse, that I might present you
    a chaste virgin to Christ.
  }
  \e{%
    Fratres: Qui gloriatur, in. Domino glorietur.
    Non enim qui seipsum commendat, ille probatus 1est, sed
    quem Deus commendat. Utinam sustineretis modicum quid
    insipientiae meae; sed et supportate me: aemulor enim vos
    Dei aemulatione. Despondi enim vos uni viro virginem
    castam exhibere Christo.
  }
}

% 
\newcommand{\responsory}{%
  Propter veritatem, et mansuetudinem, et
  justitiam: et deducet te mirabiliter dextera tua. Audi
  filia, et vide, et inclina aurem tuam: quia concupivit rex
  speciem tuam.
  Qui seminant in Iacrymis, in gaudio metent
  Euntes ibant et flebant mittentes semina sua
  Venientes autem venient cum exsultatione, portantes
  manipulos suos.
}
\newcommand{\responsoryTranslation}{%
  Because of truth and meekness, and justice; and your right hand shall conduct
  you wonderfully.  Hearken, O daughter, and see, and incline your ear, for the
  king has greatly desired your beauty.

  They who sow in tears, shall reap in joy.  they went on their way, weeping and
  scattering their seed.  But they shall surely come with joy, bringing their
  sheaves with them.
}
% 
\newcommand{\gospel}{%
  \l{%
  }
  \e{%
  }
}
\newcommand{\offertory}{%
  Filiae regum in honore tuo: astitit regina a dextris tuis in vestitu deaurato,
  circumdata varietate.
}
\newcommand{\offertoryTranslation}{%
  The daughters of kings are among your honorable attendants; at your right hand
  stands the queen in raiment of gold and embroidery of many colors.
}
\newcommand{\secret}{%
  \l{%
    Accepta tibi sit, Domine, sacratae plebis oblatio pro tuorum honore
    sanctorum, quorum se meritis de tribulatione percepisse cognoscit auxilium.
  }
  \e{%
    May this offering of Your people be accepted by You, O Lord, for the honor
    of those Your saints through whose merits they are sensible of having
    received help in their tribulations: through our Lord.
  }
}
\newcommand{\communion}{%
  Diffusa est gratia in labiis tuis: propterea benedixit te Deus in aeternum.
}
\newcommand{\communionTranslation}{%
  Grace is poured abroad in your lips; therefore has God blessed you forever.
}
\newcommand{\postcommunion}{%
  \l{%
    Satiasti, Domine, familiam tuam muneribus sacris; ejus, quaesumus, sember
    interventione nos refove, cujus solemnia celebramus.
  }
  \e{%
    You have fed  Your family with sacred gifts, O lord; refresh us always, we
    pray You, by the intercession of her whose feast we celebrate: through our Lord.
  }
  \per
}

% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../DominicanOrdinaries/masses/6/kyrie}
\newcommand{\gloriaPath}{../DominicanOrdinaries/masses/6/gloria}
\newcommand{\sanctusPath}{../DominicanOrdinaries/masses/6/sanctus}
\newcommand{\agnusPath}{../DominicanOrdinaries/masses/6/agnus}
\newcommand{\itePath}{../DominicanOrdinaries/masses/6/ite}
% 
\newcommand{\creedPath}{../DominicanOrdinaries/credo/1/credo}
% 
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
