% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{S. Hilarii Confessoris Ecclesiæ Doctoris}
% 
\newcommand{\masstype}{Missa Cantata}
\newcommand{\introittranslation}{In the midst of the Church the Lord shall open
  his mouth, filling him with the spirit of wisdom and understanding; and He
  shall clothe him with a robe of glory.}
\newcommand{\collect}{%
  \l{Deus, qui pópulo tuo ætérnæ salútis beátum Hilárium minístrum tribuísti: præsta quǽsumus; ut, quem Doctórem vitæ habúimus in terris, intercessórem habére mereámur in cælis.}
  \e{O God, Who gave to Your people blessed Hilary, as a minister of salvation, grant, we beseech You, that we who cherished him on earth as a teacher of life, may be found worthy to have him as an intercessor in heaven.}
  \l{Per Dóminum nostrum Iesum Christum, Fílium tuum: qui tecum vivit et regnat in unitáte Spíritus Sancti Deus, per ómnia sǽcula sæculórum.}
  \e{Through Jesus Christ, thy Son our Lord, Who liveth and reigneth with thee, in the unity of the Holy Ghost, God, world without end.}
  \amen
  \oremus
  \l{Concéde, quǽsumus, omnípotens Deus: ut ad meliórem vitam Sanctórum tuórum exémpla nos próvocent; quaténus, quorum sollémnia ágimus, étiam actus imitémur.}
  \e{Grant, we beseech You, almighty God, that the example of Your saints may urge us on to a better life, so that we may imitate the deeds of those whose feasts we celebrate.}
  \l{Per Dóminum nostrum Iesum Christum, Fílium tuum: qui tecum vivit et regnat in unitáte Spíritus Sancti Deus, per ómnia sǽcula sæculórum.}
  \e{Through Jesus Christ, thy Son our Lord, Who liveth and reigneth with thee, in the unity of the Holy Ghost, God, world without end.}
}
\newcommand{\responsorytranslation}{The mouth of the just shall dispense wisdom and his tongue shall speak judgment.
  The law of his God is in his heart, and his steps shall not falter. Allelúja, allelúja
  And he girded him about with a glorious girdle, and clothed him with a robe of glory, Allelúja.}
\newcommand{\lesson}{%
  \l{Caríssime: Testíficor coram Deo, et Iesu Christo, qui iudicatúrus est vivos et mórtuos, per advéntum ipsíus et regnum eius: prǽdica verbum, insta opportúne, importune: árgue, óbsecra, íncrepa in omni patiéntia, et doctrína. Erit enim tempus, cum sanam doctrínam non sustinébunt, sed ad sua desidéria, coacervábunt sibi magistros, pruriéntes áuribus, et a veritáte quidem audítum avértent, ad fábulas autem converténtur. Tu vero vígila, in ómnibus labóra, opus fac Evangelístæ, ministérium tuum ímple. Sóbrius esto. Ego enim iam delíbor, et tempus resolutiónis meæ instat. Bonum certámen certávi, cursum consummávi, fidem servávi. In réliquo repósita est mihi coróna iustítiæ, quam reddet mihi Dóminus in illa die, iustus iudex: non solum autem mihi, sed et iis, qui díligunt advéntum eius.}
  \e{Dearly beloved: I charge thee, before God and Jesus Christ, who shall judge the living and the dead, by his coming, and his kingdom: Preach the word: be instant in season, out of season: reprove, entreat, rebuke in all patience and doctrine. For there shall be a time, when they will not endure sound doctrine; but, according to their own desires, they will heap to themselves teachers, having itching ears: And will indeed turn away their hearing from the truth, but will be turned unto fables. But be thou vigilant, labour in all things, do the work of an evangelist, fulfil thy ministry. Be sober. For I am even now ready to be sacrificed: and the time of my dissolution is at hand. I have fought a good fight, I have finished my course, I have kept the faith. As to the rest, there is laid up for me a crown of justice, which the Lord the just judge will render to me in that day: and not only to me, but to them also that love his coming.}
}
\newcommand{\gospel}{%
  \l{In illo témpore: Dixit Iesus discípulis suis: Vos estis sal terræ. Quod si sal evanúerit, in quo saliétur? Ad níhilum valet ultra, nisi ut mittátur foras, et conculcétur ab homínibus. Vos estis lux mundi. Non potest cívitas abscóndi supra montem pósita. Neque accéndunt lucérnam, et ponunt eam sub módio, sed super candelábrum, ut lúceat ómnibus qui in domo sunt. Sic lúceat lux vestra coram homínibus, ut vídeant ópera vestra bona, et gloríficent Patrem vestrum, qui in cœlis est. Nolíte putáre, quóniam veni sólvere legem aut prophétas: non veni sólvere, sed adimplére. Amen, quippe dico vobis, donec tránseat cœlum et terra, iota unum aut unus apex non præteríbit a lege, donec ómnia fiant. Qui ergo solvet unum de mandátis istis mínimis, et docúerit sic hómines, mínimus vocábitur in regno cœlórum: qui autem fécerit et docúerit, hic magnus vocábitur in regno cœlórum.}
  \e{In that time Jesus said to His disciples: You are the salt of the earth. But if the salt lose its savour, wherewith shall it be salted? It is good for nothing any more but to be cast out, and to be trodden on by men. You are the light of the world. A city seated on a mountain cannot be hid. Neither do men light a candle and put it under a bushel, but upon a candlestick, that it may shine to all that are in the house. So let your light shine before men, that they may see your good works, and glorify your Father who is in heaven. Do not think that I am come to destroy the law, or the prophets. I am not come to destroy, but to fulfill. For amen I say unto you, till heaven and earth pass, one jot, or one tittle shall not pass of the law, till all be fulfilled. He therefore that shall break one of these least commandments, and shall so teach men, shall be called the least in the kingdom of heaven. But he that shall do and teach, he shall be called great in the kingdom of heaven.}
}
\newcommand{\offertorytranslation}{The just shall flourish like the palm tree: he shall grow up like the cedar of Libanus.}
\newcommand{\communiontranslation}{[This is] that faithful and wise steward, whom his lord setteth over his family, to give them their measure of wheat in due season.}
\newcommand{\postcommunion}{%
  \l{Ut nobis, Dómine, tua sacrifícia dent salútem: beátus Hilarius Póntifex tuus et Doctor egrégius, quǽsumus, precátor accédat.}
  \e{May blessed N. thy Bishop and illustrious Doctor intercede for us, O Lord, that this thy sacrifice may obtain for us salvation,}
  \l{Per Dóminum nostrum Iesum Christum, Fílium tuum: qui tecum vivit et regnat in unitáte Spíritus Sancti Deus, per ómnia sǽcula sæculórum.}
  \e{Through Jesus Christ, thy Son our Lord, Who liveth and reigneth with thee, in the unity of the Holy Ghost, God, world without end.}
  \amen
  \oremus
  \l{Quǽsumus, Dómine, salutáribus repléti mystériis: ut, beáti Félicis Mártyris tui, cuius sollémnia celebrámus, oratiónibus adiuvémur.}
  \e{Refreshed by the sacrament of salvation, we beseech You, O Lord, that we may be helped by the prayers of blessed Felix, Your Martyr, whose feast we are celebrating.}
}

\newcommand{\marian}{} % set to blank to suppress
% 


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
