% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{S. Andreæ Corsini Episcopi et Confessoris}
\newcommand{\masstype}{ Missa Cantata Iuxta Ritum Dominicanum}
% 
\newcommand{\introittranslation}{%
  The Lord made a covenant of peace with him, and made him a prince; that the
  dignity of priesthood should be his forever.  The mercies of the Lord, I will
  sing forever.
}
\newcommand{\collect}{%
  \l{%
    Deus, qui in Ecclésia tua nova semper instáuras exémpla virtútum: da pópulo tuo beáti Andréæ Confessóris tui atque Pontíficis ita sequi vestígia; ut assequátur et prǽmia.
  }
  \e{%
    O God, Who establish ever new examples of virtue in Your Church, grant that Your people may follow the footsteps of blessed Andrew, Your Confessor and Bishop, so that they may also obtain his reward.
  }
  \per
}

\newcommand{\lesson}{%
  \l{
    Ecce sacérdos magnus, qui in diébus suis plácuit Deo, et invéntus est iustus: et in témpore iracúndiæ factus est reconciliátio. Non est invéntus símilis illi, qui conservávit legem Excélsi. Ideo iureiurándo fecit illum Dóminus créscere in plebem suam. Benedictiónem ómnium géntium dedit illi, et testaméntum suum confirmávit super caput eius. Agnóvit eum in benedictiónibus suis: conservávit illi misericórdiam suam: et invénit grátiam coram óculis Dómini. Magnificávit eum in conspéctu regum: et dedit illi corónam glóriæ. Státuit illi testaméntum ætérnum, et dedit illi sacerdótium magnum: et beatificávit illum in glória. Fungi sacerdótio, et habére laudem in nómine ipsíus, et offérre illi incénsum dignum in odórem suavitátis.
  }
  \e{
Behold, a great priest, who in his days pleased God, and was found just; and in the time of wrath he was made a reconciliation. There was not found the like to him, who kept the law of the Most High. Therefore, by an oath, the Lord made him to increase among his people. He gave him the blessing of all nations, and confirmed His covenant upon his head. He acknowledged him in His blessings; He preserved for him His mercy; and he found grace before the eyes of the Lord. He glorified him in the sight of kings, and gave him a crown of glory. He made an everlasting covenant with him, and gave him a great priesthood; and made him blessed in glory. To execute the office of the priesthood, and to have praise in His name, and to offer Him a worthy incense for an odor of sweetness.
  }
}

\newcommand{\responsorytranslation}{%
  The Lord has sworn, and He will not repent: "You are a priest forever
  according to the order of Melchisedech." Yf.The Lord said to my Lord: "Sit at
  my right hand." Alleluia, alleluia!I have found David My servant; with My holy
  oil I have anointed him. Alleluia!
}

\newcommand{\gospel}{%
  \l{%
In illo témpore: Dixit Iesus discípulis suis parábolam hanc: Homo péregre proficíscens vocávit servos suos, et trádidit illis bona sua. Et uni dedit quinque talénta, álii autem duo, álii vero unum, unicuíque secúndum própriam virtútem, et proféctus est statim. Abiit autem, qui quinque talénta accéperat, et operátus est in eis, et lucrátus est ália quinque. Simíliter et, qui duo accéperat, lucrátus est ália duo. Qui autem unum accéperat, ábiens fodit in terram, et abscóndit pecúniam dómini sui. Post multum vero témporis venit dóminus servórum illórum, et pósuit ratiónem cum eis. Et accédens qui quinque talénta accéperat, óbtulit ália quinque talénta, dicens: Dómine, quinque talénta tradidísti mihi, ecce, ália quinque superlucrátus sum. Ait illi dóminus eius: Euge, serve bone et fidélis, quia super pauca fuísti fidélis, super multa te constítuam: intra in gáudium dómini tui. Accéssit autem et qui duo talénta accéperat, et ait: Dómine, duo talénta tradidísti mihi, ecce, ália duo lucrátus sum. Ait illi dóminus eius: Euge, serve bone et fidélis, quia super pauca fuísti fidélis, super multa te constítuam: intra in gáudium dómini tui.
}
  \e{%
At that time, Jesus spoke this parable to His disciples: A man going abroad, called his servants and handed over his goods to them. And to one he gave five talents, to another two, and to another one, to each according to his particular ability, and then he went on his journey. And he who had received the five talents went and traded with them, and gained five more. In like manner, he who had received the two gained two more. But he who had received the one went away and dug in the earth and hid his master’s money. Then after a long time the master of those servants came and settled accounts with them. And he who had received the five talents came and brought five other talents, saying, ‘Master, you handed over to me five talents; behold, I have gained five others in addition.’ His master said to him, ‘Well done, good and faithful servant; because you have been faithful over a few things, I will set you over many; enter into the joy of your master.’ And he also who had received the two talents came, and said, ‘Master, you handed over to me two talents; behold, I have gained two more.’ His master said to him, ‘Well done, good and faithful servant; because you have been faithful over a few things, I will set you over many; enter into the joy of your master.’
}
}
\newcommand{\offertorytranslation}{%
  The just man shall flourish like the palm tree; he shall grow up like the cedar of Lebanon: in the house of the Lord.
}
\newcommand{\communiontranslation}{%
  Blessed is that servant, whom, when the Lord shall come, He shall find watching. Amen I say to you, he will set him over all His goods.
}
\newcommand{\postcommunion}{%
  \l{%
    Da, quaesumus Domine, fidelibus tuis, sanctorum tuorum semper veneratione laetari, et eorum perpetua supplicatione muniri.
  }
  \e{%
    Grant to Your faithful, we beseech You, 0 Lord, ever to be gladdened by the veneration of Your saints, and to be fortified by their interceding prayer: through out Lord.
  }
  \per
}

% 
% File paths: we don't use symlinks as (a) not all platforms support them, and
% (b) they don't fit nicely with the flow we're using.

\newcommand{\kyriePath}{../DominicanOrdinaries/masses/3/kyrie}

\newcommand{\gloriaPath}{../DominicanOrdinaries/masses/3/gloria}
\newcommand{\sanctusPath}{../DominicanOrdinaries/masses/3/sanctus}
\newcommand{\agnusPath}{../DominicanOrdinaries/masses/3/agnus}
\newcommand{\itePath}{../DominicanOrdinaries/masses/3/ite}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
