% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{S. Stanislai, Episcopi et Martyris}
% 
\newcommand{\masstype}{Missa Cantata}
\newcommand{\introittranslation}{
  The just man shall rejoice in the Lord, and shall hope in Him; and all the
  upright of heart shall be praised. Alleluia, alleluia! Hear, O God,
  my prayer when I make supplication to Thee; deliver my soul from the fear of
  the enemy. Glory.
}
\newcommand{\collect}{%
  \l{
    Deus, pro cujus honore gloriosus pontifex Stanislaus gladiis impiorum
    occubuit: praesta quaeswnus, ut omnes, qui ejus implorant auxilium,
    petitionis suae salutarem consequantur effectum.
  }
  \e{
    O God, for whose honor the glorious bishop Stanislaus was slain by the
    swords of wicked men; grant, we beseech You, that such as seek his help
    may obtain a happy issue of their prayer.
  }
}
\newcommand{\lessontranslation}{
  How boldly, then, will the just man appear, to meet his old persecutors, that
  thwarted all his striving!  And they, in what craven fear they will cower at
  the sight of him, amazed at the sudden reversal of his fortunes!  Inward
  remorse will wring a groan from those hearts: Why, these were the men we made
  into a laughing-stock and a by-word!  We, poor fools, mistook the life they
  lived for madness, their death for ignominy; and now they are reckoned as
  God’s own children, now it is among his holy ones that their lot is cast.
}
\newcommand{\responsorytranslation}{

  Alleluia, alleluia. The just man shall rejoice in the Lord, and shall hope in
  Him, and all the upright in heart shall be praised.

  Alleluia! An angel of the Lord came down from heaven; and drawing near, rolled
  back the stone, and sat upon it. Alleluia!
}
\newcommand{\gospel}{%
  \l{
    Ego sum vitis vera, et Pater meus agricola est. Omnem palmitem in me non
    ferentem fructum, tollet eum, et omnem qui fert fructum, purgabit eum, ut
    fructum plus afferat. Jam vos mundi estis propter sermonem quem locutus sum
    vobis. Manete in me, et ego in vobis. Sicut palmes non potest fere fructum a
    semetipso, nisi manserit in vite, sic nec vos, nisi in me manseritis. Ego
    sum vitis, vos palmites: qui manet in me, et ego in eo, hic fert fructum
    multum, quia sine me nihil potestis facere. Si quis in me non manserit,
    mittetur foras sicut palmes, et arescet, et colligent eum, et in ignem
    mittent, et ardet. Si manseritis in me, et verba mea in vobis manserint,
    quodcumque volueritis petetis, et fiet vobis.
  }
  \e{
    I am the true vine, and it is my Father who tends it. The branch that yields
    no fruit in me, he cuts away; the branch that does yield fruit, he trims
    clean, so that it may yield more fruit. You, through the message I have
    preached to you, are clean already; you have only to live on in me, and I
    will live on in you. The branch that does not live on in the vine can yield
    no fruit of itself; no more can you, if you do not live on in me. I am the
    vine, you are its branches; if a man lives on in me, and I in him, then he
    will yield abundant fruit; separated from me, you have no power to do
    anything. If a man does not live on in me, he can only be like the branch
    that is cast off and withers away; such a branch is picked up and thrown
    into the fire, to burn there. As long as you live on in me, and my words
    live on in you, you will be able to make what request you will, and have it
    granted.
  }
}
\newcommand{\offertorytranslation}{
  You have crowned him with glory and honor, and have set him over the works of
  Your hands, O Lord, alleluia!
}
\newcommand{\communiontranslation}{
  He who wishes to come after Me, let him deny himself, and take up his cross,
  and follow Me, alleluia!
}
\newcommand{\postcommunion}{%
  \l{
    Satiasti, Domine, familiam tuam muneribus sacris: beati Stanislai martyris
    tui atque pontificis, quaesumus, semper interventione nos refove, cujus
    solemnia celebramus.
  }
  \e{
    Thou hast nourished Thy family with holy gifts, I Lord; quicken us we pray
    Thee, through the constant help of blessed Stanislaus, Thy martyr and
    bishop, whose feast we keep.
  }
}

\newcommand{\marian}{} % set to blank to suppress
% 


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
