% This file defines the propert to be inserted into missalette.tex  In this way
% multiple feasts can be typeset very quickly.  missalette.tex should not normally
% need changing.  Note that this is not the most readable way to insert text
% into a LaTeX document, but it is the most powerful: the macros defined here
% are directly excecuted when building the document.

% For the title page
\newcommand{\feast}{S. Bibianiae Virg. et Mart.}
% 
\newcommand{\masstype}{Missa Cantata iuxta Ritum Dominicanum}

\newcommand{\introittranslation}{Let us all rejoice in the Lord, celebrating the
  feast in honor of blessed Agatha, Virgin and Martyr, for whose passion the
  angels rejoice and praise with one accord the Son of God.  \emph{Ps.} My heart
  overflows with a goodly theme; as I sing my ode to the King.}

\newcommand{\collect}{%
  \l{Deus, qui inter cétera poténtiæ tuæ mirácula étiam in sexu frágili
    victóriam martýrii contulísti: concéde propítius; ut, qui beátæ Agathæ
    Vírginis et Mártyris tuæ natalítia cólimus, per eius ad te exémpla
    gradiámur.}

  \e{O God, Who among other wonders of Your power have given the victory of
    martyrdom even to the gentler sex, graciously grant that we who commemorate
    the anniversary of the death of blessed Agatha, Your Virgin and Martyr, may
    come to You by following her example.}

  \l{Per Dóminum nostrum Iesum Christum, Fílium tuum: qui tecum vivit et regnat
    in unitáte Spíritus Sancti Deus, per ómnia sǽcula sæculórum.}

  \e{Through Jesus Christ, thy Son our Lord, Who liveth and reigneth with thee,
    in the unity of the Holy Ghost, God, world without end.}
}

\newcommand{\lesson}{
  \l{Léctio Epístolæ beáti Pauli Apóstoli ad Corinthios}

  \e{Léctio Epístolæ beáti Pauli Apóstoli ad Corinthios}

  \l{Fratres: Vidéte vocatiónem vestram: quia non multi sapiéntes secúndum
    carnem, non multi poténtes, non multi nóbiles: sed quæ stulta sunt mundi
    elégit Deus, ut confúndat sapiéntes: et infírma mundi elégit Deus, ut
    confúndat fórtia: et ignobília mundi et contemptibília elégit Deus, et ea
    quæ non sunt, ut ea quæ sunt destrúeret: ut non gloriétur omnis caro in
    conspéctu eius. Ex ipso autem vos estis in Christo Iesu, qui factus est
    nobis sapiéntia a Deo, et iustítia, et sanctificátio, et redémptio: ut,
    quemádmodum scriptum est: Qui gloriátur, in Dómino gloriétur.}

  \e{Brethren: Consider your own call, that there were not many wise according
    to the flesh, not many mighty, not many noble. But the foolish things of the
    world has God chosen to put to shame the wise, and the weak things of the
    world has God chosen to put to shame the strong, and the base things of the
    world and the despised has God chosen, and the things that are not, to bring
    to naught the things that are; lest any flesh should pride itself before
    Him. From Him you are in Christ Jesus, Who has become for us God-given
    wisdom, and justice, and sanctification, and redemption; so that, just as it
    is written, Let him who takes pride, take pride in the Lord.}
}


\newcommand{\responsorytranslation}{God will help her with His countenance. God
  is in her midst; she shall not be disturbed.  \v. There is a stream whose
  runlets gladden the city of God; the Most High has sanctified His
  dwelling. Alleluia, alleluia.  \v. I will speak of Your decrees
  before kings without being ashamed. Alleluia.}

\newcommand{\gospel}{%
  \l{In illo témpore: Accessérunt ad Iesum pharisǽi, tentántes eum et dicéntes:
    Si licet hómini dimíttere uxórem suam quacúmque ex causa? Qui respóndens,
    ait eis: Non legístis, quia, qui fecit hóminem ab inítio, másculum et
    féminam fecit eos? et dixit: Propter hoc dimíttet homo patrem, et matrem, et
    adhærébit uxóri suæ, et erunt duo in carne una. Itaque iam non sunt duo, sed
    una caro. Quod ergo Deus coniúnxit, homo non séparet. Dicunt illi: Quid ergo
    Móyses mandávit dare libéllum repúdii, et dimíttere? Ait illis: Quóniam
    Móyses ad durítiam cordis vestri permísit vobis dimíttere uxóres vestras: ab
    inítio autem non fuit sic. Dico autem vobis, quia, quicúmque dimíserit
    uxórem suam, nisi ob fornicatiónem, et áliam dúxerit, mœchátur: et qui
    dimíssam duxerit, mœchátur. Dicunt ei discípuli eius: Si ita est causa
    hóminis cum uxore, non expedit nubere. Qui dixit illis: Non omnes cápiunt
    verbum istud, sed quibus datum est. Sunt enim eunúchi, qui de matris útero
    sic nati sunt; et sunt eunúchi, qui facti sunt ab homínibus; et sunt
    eunúchi, qui seípsos castravérunt propter regnum cœlórum. Qui potest cápere,
    cápiat.}

  \e{At that time, there came to Jesus some Pharisees, testing Him, and saying,
    Is it lawful for a man to put away his wife for any cause? But He answered
    and said to them, Have you not read that the Creator, from the beginning,
    made them male and female, and said, ‘For this cause a man shall leave his
    father and mother, and cleave to his wife, and the two shall become one
    flesh’? Therefore now they are no longer two, but one flesh. What therefore
    God has joined together, let no man put asunder. They said to Him, Why then
    did Moses command to give a written notice of dismissal, and to put her
    away? He said to them, Because Moses, by reason of the hardness of your
    heart, permitted you to put away your wives; but it was not so from the
    beginning. And I say to you, that whoever puts away his wife, except for
    immorality, and marries another, commits adultery; and he who marries a
    woman who has been put away commits adultery. His disciples said to Him, If
    the case of a man with his wife is so, it is not expedient to marry. And He
    said, ‘Not all can accept this teaching; but those to whom it has been
    given. For there are eunuchs who were born so from their mother’s womb; and
    there are eunuchs who were made so by men; and there are eunuchs who have
    made themselves so for the sake of the kingdom of heaven. Let him accept it
    who can.}
}

\newcommand{\offertorytranslation}{Behind her the virgins of her train are
  brought to the King. They are borne in to You.}

\newcommand{\communiontranslation}{I invoke Him, the living God, Who deigned to
  cure me of every wound, and to restore my breast to my body.}

\newcommand{\postcommunion}{%
  \l{Auxiliéntur nobis, Dómine, sumpta mystéria: et, intercedénte beáta Agatha
    Vírgine et Mártyre tua, sempitérna protectióne confírment.}

  \e{May the sacrament we have received help us, O Lord, and by the intercession
    of blessed Agatha, Your Virgin and Martyr, may it support us through Your
    everlasting protection.}
  
  \l{Per Dóminum nostrum Iesum Christum, Fílium tuum: qui tecum vivit et regnat
    in unitáte Spíritus Sancti Deus, per ómnia sǽcula sæculórum.}
  
  \e{Through Jesus Christ, thy Son our Lord, Who liveth and reigneth with thee,
    in the unity of the Holy Ghost, God, world without end.}
}

\newcommand{\marian}{} % set to blank to suppress
% 

% Ordinary
\newcommand{\kyrie}{vi}
\newcommand{\gloria}{} % set to blank to suppress
\newcommand{\sanctus}{xiv}
\newcommand{\agnus}{xiv}


%%% Local Variables:
%%% mode: latex
%%% TeX-master: "missalette"
%%% End:
